---
title: "TestSmoothnessEffects"
author: "ML"
date: "12/22/2020"
output: html_document
---

You probably downloaded all files from 
`github("IPEM/BListener_supplementary_material")`
in you current working directory

First we add some libraries, including `BListener`.
Be sure that you also have `BLplot.R` in the present directory.

```{r, echo=FALSE}
library(reshape2)
library(tseries)
library(ggplot2)
library(gridExtra)
library(grid)
library(GGally)
### Prepare functions of BListener package an other
library(BListener)
source("./BLplot.R")
```

First we generate a sinusoidal signal consisting of 75 data points. Then we generated 75 random numbers using a normal distribution with zero mean and standard deviation of 15% of the y-value of the sinusoid. These numbers were then added to the sinusoidal signal and the resulting values served as duration values of IOI-observed objects. We transformed these values to milliseconds so that they could be used as input to the Bayesian listener algorithm (dots in Figure 2, left panels). The goal is to retrieve a sinusoid-like IOI-class time series from the IOI-observed objects, using different values for V_t and W_t.

```{r}
# create a sinusoidal signal
times = seq(from=1,to=75)/75  # length.out=lenn) # we create a time sequence
cy <- 8 + .5*sin(2*pi*times)  # 2^8 milliseconds, half octave up and octave half down in log2dur
# add .15 sd noise
set.seed(134)
oy = rnorm(75,0,.15)  # sd of .15
oy[1] = 0  # to have a controlled beginning
r = oy + cy
cr = cumsum(r)
plot(r~cr,xlab="object",ylab="IOI (log2dur)")
lines(cy ~ cr)
```

Translate to milliseconds and generate u, the input to BListener
```{r}
rr <- as.numeric(t(2^r))
u <- 2^r
plot(cumsum(u)/1000,u, xlab="time in sec.",ylab="IOI (msec.)")
```

Apply BListener
```{r}
R1 <- BLmain(u,meter=1,V =.0000001,W=0.01)
Post1 <- BLpost(R1)
pl1 <- BLplot(R1,0)
R2 <- BLmain(u,meter=1,V=.00001,W=0.001)
Post2 <- BLpost(R2)
pl2 <- BLplot(R2,0)
R3 <- BLmain(u,meter=1,V=.001,W=0.00001)
Post3 <- BLpost(R3)
pl3 <- BLplot(R3,0)
#### Diagnostic 
pll <- list()
for (ii in 1:3) {
  if(ii == 1) R <- R1
  if(ii == 2) R <- R2
  if(ii == 3) R <- R3
  I <- as.data.frame(cbind(R1$Timeline,R$Innovation))#,Name))
  colnames(I) <- c("Timeline","Innovation")
  Imelted <- melt(I,id=c("Timeline"))#,"Name"))
  diagplot1 <- ggplot() + 
    geom_point(data=Imelted,aes(x=Timeline,y=value,shape=factor(variable)),size=1.5) +
    theme_bw() +
    theme(legend.position="none")+
    labs(y = "IOI (log2dur)" , x="time (sa)")+
    geom_line(data=Imelted, aes(x=Timeline,y=Timeline*0),size=.7)
  #https://stackoverflow.com/questions/4357031/qqnorm-and-qqline-in-ggplot2
  qqplot.data <- function (vec) # argument: vector of numbers
  {
    # following four lines from base R's qqline()
    y <- quantile(vec[!is.na(vec)], c(0.25, 0.75))
    x <- qnorm(c(0.25, 0.75))
    slope <- diff(y)/diff(x)
    int <- y[1L] - slope * x[1L]
    d <- data.frame(resids = vec)
    ggplot(d,aes(sample=resids))+stat_qq()+geom_abline(slope=slope,intercept=int)
  }
  diagplot2 <- qqplot.data(Imelted$value) + theme_bw()
  pll[[ii]] = list(diagplot1,diagplot2)
}
# grid.arrange(
#   pl1,pll[[1]][[1]],pll[[1]][[2]],
#   pl2,pll[[2]][[1]],pll[[2]][[2]],
#   pl3,pll[[3]][[1]],pll[[3]][[2]],
#   ncol=3)
F1 <- rbind(
  Post1$Fluctuation1,
  Post2$Fluctuation1,
  Post3$Fluctuation1)
colnames(F1) <- "Fluctuation1"
row1 = print(paste('r =',Post1$parameters$V/Post1$parameters$W))
row2 = print(paste('r =',Post2$parameters$V/Post2$parameters$W))
row3 = print(paste('r =',Post3$parameters$V/Post3$parameters$W))
rownames(F1) <- c(row1,row2,row3)
S <- rbind(
  Post1$Stability,
  Post2$Stability,
  Post3$Stability)
colnames(S) <- "Stability"
F2 <- rbind(
  Post1$Fluctuation2,
  Post2$Fluctuation2,
  Post3$Fluctuation2)
colnames(F2) <- "Fluctuation2"
g1  <- tableGrob(round(F1,digits=2))
g2  <- tableGrob(round(F2,digits=2))
g3  <- tableGrob(round(S,digits=2))
grid.newpage()
grid.arrange(arrangeGrob(
  pl1,pll[[1]][[1]],pll[[1]][[2]],
  pl2,pll[[2]][[1]],pll[[2]][[2]],
  pl3,pll[[3]][[1]],pll[[3]][[2]],
  g1,g2,g3 , ncol=3 ) )
```

The following is  producing a tiff

```{r}
bitmap("Figure2.tiff", height = 5, width = 7, res=1200)
grid.arrange(arrangeGrob(
  pl1,pll[[1]][[1]],pll[[1]][[2]],
  pl2,pll[[2]][[1]],pll[[2]][[2]],
  pl3,pll[[3]][[1]],pll[[3]][[2]],
  g1,g2,g3, ncol=3))
dev.off()
par(mfrow = c(1,1))
```
